\tool: Programmable and Efficient Secure Two-Party Computation for Machine Learning

### 2018-08-07 ndss/conclude.tex
added ndss version.
comments from the email
nits in cryptographic cost aware

We presented \tool, the first
cryptographic-cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to, or better than the previously known custom specialized
protocols from previous works.
The compiler is backed by formal semantics that help 
%it
%insert type coercions between boolean and arithmetic parts automatically while 
it maintain correctness, security,
and efficiency.

Currently, we are working on a front-end to translate Tensorflow code to \tool. The aim here is to provide a push button implementation  that generates secure implementations for existing Tensorflow models.  
In the future, we would like to extend our security guarantees to malicious adversaries. 
 The cryptographic backends continue to improve and the modular design of \tool makes it easy to integrate with the best available backends.
However, we are currently unaware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits.
Finally, we will explore the possibility of mechanically verifying the  compiler implementation.

>>>>

We presented \tool, the first
cryptographic cost aware framework that generates efficient and
scalable \mpc protocols from high-level programs.
The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to, or better than the previously known custom specialized
protocols from previous works.
The compiler is backed by formal semantics that help 
%it
%insert type coercions between boolean and arithmetic parts automatically while 
it maintain correctness, security,
and efficiency.

Currently, we are working on a front-end to translate Tensorflow code
to \tool. The aim here is to provide a push button implementation
that generates secure implementations for existing Tensorflow models. 
In the future, we would like to extend our security guarantees to
malicious adversaries. We think that, with suitable
changes to operator costs, \tool can target other backends including 3PC or
MPC, or protocols secure against malicious adversaries.
 The cryptographic backends continue to improve and the modular design of \tool makes it easy to integrate with the best available backends.
However, we are currently unaware of a maliciously secure \mpc implementation for combinations of
arithmetic and boolean circuits.
Finally, we will explore the possibility of mechanically verifying the  compiler implementation.

### 2018-08-07 ndss/eval.tex
nits in cryptographic cost aware

%dataset | time | comm | timeL | timeW | comm
%Our decision tree numbers in Table~\ref{tab:dt} further validate
%this claim. 
%We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
%describe specialized protocols for trees and forests (that perform
%better than~\cite{shafindss}).
%Similar to Bost et al.~\cite{shafindss}, they also remarks that these
%computations are infeasible with Yao-based 2PC.
%Again, we observe that
%the performance of \tool generated generic 2PC
%code is competitive with specialized protocols. 
The results for Na\"{i}ve Bayes are
in Table~\ref{tab:nb}. As before, $n$ denotes the number of classes and $F$ is the number of features.
%Although, there are no multiplications in these benchmarks, these do
%have a significant number of comparisons (due to array look-ups using
%secret indices) that
%result in many boolean-and gates. %(13k/750k denote 13000/75000). 
As before, we compare with Bost et al.~\cite{shafindss} and observe that \tool generated code
has better performance, despite using a generic 2PC,
as opposed to custom designed protocols developed by Bost et
al. Moreover, they remark that in their setup, generic Yao-based 2PC
did not scale to the smallest of their Na\"{i}ve Bayes classifiers, so
they had to scale down the prediction task, and even then Yao-based \mpc
was 500x slower. Whereas, we show that by using a
cryptographic-cost aware compiler, we can scale generic 2PC to real
prediction tasks, and get performance competitive to or better than the
specialized protocols. Table~\ref{tab:dt} 
compares against the more recent work of~\cite{wu}
on decision trees and further validates this claim.

>>>>

%dataset | time | comm | timeL | timeW | comm
%Our decision tree numbers in Table~\ref{tab:dt} further validate
%this claim. 
%We compare with the recent work of Wu et al.~\cite{wu} (columns 3 and 4) who
%describe specialized protocols for trees and forests (that perform
%better than~\cite{shafindss}).
%Similar to Bost et al.~\cite{shafindss}, they also remarks that these
%computations are infeasible with Yao-based 2PC.
%Again, we observe that
%the performance of \tool generated generic 2PC
%code is competitive with specialized protocols. 
The results for Na\"{i}ve Bayes are
in Table~\ref{tab:nb}. As before, $n$ denotes the number of classes and $F$ is the number of features.
%Although, there are no multiplications in these benchmarks, these do
%have a significant number of comparisons (due to array look-ups using
%secret indices) that
%result in many boolean-and gates. %(13k/750k denote 13000/75000). 
As before, we compare with Bost et al.~\cite{shafindss} and observe that \tool generated code
has better performance, despite using a generic 2PC,
as opposed to custom designed protocols developed by Bost et
al. Moreover, they remark that in their setup, generic Yao-based 2PC
did not scale to the smallest of their Na\"{i}ve Bayes classifiers, so
they had to scale down the prediction task, and even then Yao-based \mpc
was 500x slower. Whereas, we show that by using a
cryptographic cost aware compiler, we can scale generic 2PC to real
prediction tasks, and get performance competitive to or better than the
specialized protocols. Table~\ref{tab:dt} 
compares against the more recent work of~\cite{wu}
on decision trees and further validates this claim.

### 2018-08-07 ndss/ex.tex
nits in cryptographic cost aware

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression (the '? :' operator) computation are more efficient in the
boolean representation, the \tool compiler uses the Yao circuit
builder \ls{ycirc} to build the corresponding comparison and
multiplexer circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}). In our usage
of ABY, boolean is synonymous with Yao, we elaborate in
\sectionref{impl}.

@@

%% \subsection{Cryptographic cost-aware compiler}
%% \label{sec:ccc}
%% One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
%% As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean ($\sim9x$ more time $\&$ $\sim20x$ more communication in a LAN setting). Since the performance gap between arithmetic and boolean multiplication is quite large, we believe that this choice is optimal for realistic network settings.
%% However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
%% Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
%% We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use heuristics based on costs observed using microbenchmarking. 
%% For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
%% generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

>>>>

Within the secret components, the \tool compiler is ``cryptographic
cost aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression (the '? :' operator) computation are more efficient in the
boolean representation, the \tool compiler uses the Yao circuit
builder \ls{ycirc} to build the corresponding comparison and
multiplexer circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}). In our usage
of ABY, boolean is synonymous with Yao, we elaborate in
\sectionref{impl}.

@@

%% \subsection{Cryptographic cost aware compiler}
%% \label{sec:ccc}
%% One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
%% As mentioned above, \tool is a cryptographic cost aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean ($\sim9x$ more time $\&$ $\sim20x$ more communication in a LAN setting). Since the performance gap between arithmetic and boolean multiplication is quite large, we believe that this choice is optimal for realistic network settings.
%% However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
%% Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
%% We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use heuristics based on costs observed using microbenchmarking. 
%% For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
%% generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.
